SubsidyExplorer - Step 2: Create Vessel List

### 2020-03-20 scripts/02_vessel_list.Rmd

SELECT
  *,
  CASE
    WHEN engine_power_kw IS NULL THEN fishing_hours_lat_lon
    ELSE fishing_hours_lat_lon*engine_power_kw
  END AS fishing_KWh_lat_lon
FROM
  fishing_by_lat_lon
LEFT JOIN
  vessel_info
USING
  (ssvid,
  year)
'

>>>>

SELECT
  *,
  CASE
    WHEN engine_power_kw IS NULL THEN fishing_hours_lat_lon*400
    ELSE fishing_hours_lat_lon*engine_power_kw
  END AS fishing_KWh_lat_lon
FROM
  fishing_by_lat_lon
LEFT JOIN
  vessel_info
USING
  (ssvid,
  year)
'
